### 2020-06-21 magic_paper.tex
Mainly worked on Lemma 8 and section VI

Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\mbox{\tiny max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr [ L\rho] \ge 0$ with $L \in \mathcal{B}(\mathcal{H})$.
\nick{Unfortunately, this is not enough. 
There are positive Wigner ditributions which correspond to invalid states i.e. they are NOT positive semi-definite.
Therefore, there are ``holes'' in the set specified by these linear constraints.
We need a stricter argument.}

@@

The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
Completely positive-Wigner-preserving operations~\cite{cit:wang} form the operation class $\Omax$.
Therefore, $\sigma$--fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
In particular, the stabilizer operations $\so$ are contained within $\Omax$.
\begin{figure}[t]
    \centering
        \includegraphics[scale=0.47
        ]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
    Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations) involve operations within the yellow regions, with all other established magic theories between these two.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$ with each one extendible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment $\bmd$-majorization can be used allowing for an \nick{in-depth approach} towards the study of magic state interconversion.
    }
    \label{fig:zoo}
\end{figure}

@@

A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
Let the vector $\bmz^\downarrow$ denote a component permutation of vector $\bmz \in \reals^d$, so that its components are arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmz \in \reals^d$.
    Let $\bmd \in \reals^d$ be a vector with positive components, $\pi$ a permutation mapping $(z_i/d_i) \mapsto (z_\pi(i)/d_\pi(i)) \coloneqq (z_i/d_i)^\downarrow$ for all $i=1,\dots,d$ and $D = \sum_{i=1}^d d_i$.

    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$,where
    \begin{equation}\label{eq:lorenz}
        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
    \end{equation}
    The Lorenz curve of vector $\bmz$ with respect to $\bmd$ is then $\lc{\bmz}{\bmd}(x)$ for all $x \in [0,1]$.
\end{definition}
\nick{The discrete formulation is more useful in the whole discussion that follows, but the functional formulation is a little more elegant - what to choose?}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, one can see that the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $D(\frac{z_i}{d_i})^\downarrow$ for $i=1,\dots,d$ which is non-increasing by construction.

@@

We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
\begin{proposition}\label{thm:lccont}
	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$. 
	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
	I think this clears up the narrative quite a bit? - Should we keep and prove this result?}
\end{proposition}
The proof of this important result is in \nick{the appendix}.
The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
Therefore, Lorenz curves and majorization analysis in general \nick{behave nicely in the presence of / are robust under} imperfections in the experimental implementation of quantum operations.
In particular, any $\sigma_0$--fragment defined by a non full-rank state $\sigma_0$ can be approximated by a $\sigma$--fragment defined by a full-rank $\sigma$ which is arbitrarily close to $\sigma_0$, such that $\sigma = (1-\epsilon)\sigma_0 + \epsilon\frac{1}{d}\id$, for some small $\epsilon > 0$.
Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.

@@

It can further be seen that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ \nick{CITE}, defined as the sum of the negative components in $\W{\rho}$.
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	\nick{Proof}
\end{proof}

Therefore, it is clear that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity ($\rm{sn}$) further discussed in \nick{expand - move subsection on monotones (\cref{sec:mono}) in intro}.
Moreover, the area $\A_\sigma(\rho)$ of the function $L_{\rho|\sigma}$ above the line $y=1$ is also a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}

@@

Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
As a simple example, the dephasing channel
\begin{equation}
	\Delta(\rho) = \sum_{k \in \zd} \ketbra{k}{k}\rho\ketbra{k}{k}
\end{equation}
removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
If the circuit simply consists of such dephasing channels, the whole analysis can be restricted in the $\sigma$--fragments for pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.

@@

Consider a general magic state distillation process, \nick{Generalise discussion to any state conversion?}
\begin{equation}\label{eq:distprocess}
    \rho^{\otimes k} \longrightarrow \tau,
\end{equation}
where $k$ noisy copies of magic state $\rho$ are converted to a single-copy magic state $\tau$.

It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a bound for the process,
\begin{equation}
    \mana{\rho} \geq \frac{1}{k} \mana{\tau}.
\end{equation}

A new bound can be obtained in every $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
\begin{equation}\label{eq:majbound}
    L_k(\rho^{\otimes k} | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2.
\end{equation}
If the Lorenz curve of the initial state is below the target curve at any point, the process is not possible.
In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ are calculated, along with their multiplicities, by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
This follows from the multiplicativity of the Wigner distribution.

As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_j{L_j \left( \ketbra{S}^{\otimes k} \bigm| \sigma \right)} = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j: 1 \leq 2j+1 \leq k} 4^{-(2j+1)} \binom{k}{2j+1}.
\end{equation}
\ddd{[We can probably put upper and lower bounds on this value fairly readily. E.g. using known sum rules. Also -- bad choice of variable $k$, using it as index and also copy number. I think $L_{\rho|\sigma}$ is a neater formulation, since you then package things into a single object -- a function.]}

Consider the noisy Strange state,
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in the $\sigma$--fragment $\O_\sigma$.
At any noise level $\epsilon \leq \frac{3}{4}$, the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ contains negativities and the state can be purified so as to obtain a single-copy state with sufficiently low $\epsilon$.
In~\cref{fig:distill}, we examine the purifying process 
\begin{equation}\label{eq:purify}
    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
\end{equation}
with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds \nick{threshold/bound? need to define the notion of a bound precisely}.
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/ratios.pdf}
    \caption{\textbf{Noise threshold ratios.} Mana and Lorenz curve ratios for the Strange state purifying process in~\cref{eq:purify}.
    The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
    \nick{Consider set of pure stabilizer states instead of $(1-p)\ketbra{0} + p \frac{1}{3}\id$ perhaps}
    }
    \label{fig:distill}
\end{figure}

In fact, we can more generally claim that mana bounds are always weaker than bounds provided by Lorenz curve comparison for any magic state interconversion.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, $\W{\sigma}$--majorization provides a stricter bound than mana in any $\sigma$--fragment.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed monotonically in terms of mana,
    \begin{equation}
        \max_k{L_k(\rho | \sigma)} = 1 + \sum_{\bmz: \W[\bmz]{\rho}<0} \abs{\W[\bmz]{\rho}} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the $\W{\sigma}$--majorization condition
    \begin{equation}
    	L_k(\rho | \sigma) \geq L_k (\tau | \sigma),\ k=1,\dots,d^2
    \end{equation}
    implies the mana condition $\mana{\rho} \geq \mana{\tau}$.

@@

\subsection{Magic in thermal fragments}

\nick{$\rcu$ and Noisy channels preserve $\frac{1}{d}\id$}

\nick{Can extend to general thermal states}

>>>>

Any magic theory $\R = (\F, \O)$ is a subtheory of $\Rmax$ as explained in~\cref{sec:intro}, and as such it falls under this new stochasticity setting. 
For technical simplicity in what follows we assume that $\F$ is a closed set, and note that $\F_{\rm{ max}}$ is itself a closed set, since it is specified by a finite set of linear constraints of the form $\tr[ L\rho] \geq 0$ with $L \in \cal{B}(\cal{H})$, ensuring that the state is positive as well as Wigner-positive.

@@

The zoo of all magic operation classes is summarised in ~\cref{fig:zoo}.
Completely positive-Wigner-preserving operations~\cite{cit:wang} form the operation class $\Omax$.
Therefore, $\sigma$--fragments cover this theory of magic exactly and any magic subtheory is contained within this cover.
In particular, the stabilizer operations $\so$ are contained within $\Omax$.
\begin{figure}[t]
    \centering
        \includegraphics[scale=0.47
        ]{figs/operations.pdf}
    \caption{\textbf{Decomposition of a magic theory $\R$ intro $\sigma$--fragments.} 
    Examples of magic theories ($\so$: Stabilizer operations, $\Omax$: Completely positive-Wigner-preserving operations, $\rcu$: Random Clifford Unitaries -- subclass of $\so$) involve operations within the yellow regions, with all other established magic theories between these two.
    We introduce $\sigma$--fragments $\O_\sigma$ defined for all free states $\sigma$ that cover $\Omax$ with each one extendible to a set of stochastic maps outside the $\cptp$ operations.
    Within each $\sigma$--fragment $\bmd$-majorization can be used allowing for an \nick{in-depth approach} towards the study of magic state interconversion.
    }
    \label{fig:zoo}
\end{figure}

@@

A numerically efficient reformulation of $\bmd$-majorization is provided by Lorenz curves.
Let the vector $\bmu^\downarrow$ denote the vector $\bmu \in \reals^d$ with its components arranged in non-increasing order.
\begin{definition}[\textbf{Lorenz curve}]\label{def:lc}
    Let $\bmz, \bmd \in \reals^d$, where the components of $\bmd$ are positive with $D = \sum_{i=1}^d d_i$ and denote by $\bmu \coloneqq (z_1/d_1, \dots, z_d/d_d)^T$ the vector of ratios between the corresponding components of $\bmz$ and $\bmd$.

    Finally, denote by $\pi: \zd \mapsto \zd$ the permutation that sorts $\bmu$, $(\bmu^\downarrow)_i = u_{\pi(i)}$ for all $i=1,\dots,d$.

    Consider the piecewise linear curve obtained by joining the points $\{(0,0)\} \cup \{ (x_k, \lc{\bmz}{\bmd}(k)) \}_{k=1,\dots,d}$, where
    \begin{equation}\label{eq:lorenz}
        (x_k, \lc{\bmz}{\bmd}(k)) \coloneqq \left( \frac{1}{D}\sum_{i=1}^k d_{\pi(i)}, \sum_{i=1}^k z_{\pi(i)} \right) \in \mathbb{R}^2.
    \end{equation}
    The \emph{Lorenz curve} of vector $\bmz$ with respect to $\bmd$ is then $\lc{\bmz}{\bmd}(x)$ for all $x \in [0,1]$

    Expressed explicitly,
    \begin{equation}
		\lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i x + \lc{\rho}{\sigma}(i) - (\bmu^\downarrow)_i x_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d$ with $x_0 \coloneqq 0$.
\end{definition}
\nick{The discrete formulation is more useful in the whole discussion that follows, but the functional formulation is a little more elegant - what to choose?}
Components $x_k$ are rescaled by $D$ so that comparison of curves with unequal dimensions is possible.
In fact, the Lorenz curves $\lc{\bmz}{\bmd}$ and $\lc{\bmz \otimes \bmd}{\bmd \otimes \bmd}$, where $\otimes$ denotes the Kronecker product, are identical.
Furthermore, a Lorenz curve $\lc{\bmz}{\bmd}(x)$ is always concave in $x$, since it consists of $d$ line segments each with slope $(\bmu^\downarrow)_i$ for $i=1,\dots,d$ which is non-increasing by definition.

@@

We now establish important properties of Lorenz curves that are independent of the $\sigma$--fragment they are defined in.
\begin{proposition}\label{thm:lccont}
	The Lorenz curve $\lc{\rho}{\sigma}(x)$ of a state $\rho$ with respect to state $\sigma$ is uniformly continuous in $\sigma$. 
	\nick{In the sense that if $\sigma$ and $\sigma'$ are $\delta$-close with respect to a state norm, then the curves $\lc{\rho}{\sigma}(x)$ and $\lc{\rho}{\sigma'}(x)$ are $\epsilon$-close at all $x \in [0,1]$.
	I think this clears up the narrative quite a bit? - Should we keep and prove this result?}
\end{proposition}
The proof of this important result is in \nick{the appendix}.
The consequence of this statement is that infinitesimal changes in state $\sigma$ only result in infinitesimal shifts of the $\sigma$--fragment.
Therefore, Lorenz curves and majorization analysis in general \nick{behave nicely in the presence of / are robust under} imperfections in the experimental implementation of quantum operations.
In particular, any $\sigma_0$--fragment defined by a non full-rank state $\sigma_0$ can be approximated by a $\sigma$--fragment defined by a full-rank $\sigma$ which is arbitrarily close to $\sigma_0$, such that $\sigma = (1-\epsilon)\sigma_0 + \epsilon\frac{1}{d}\id$, for some small $\epsilon > 0$.
Such $\sigma_0$--fragments may include important stabilizer operations such that the replacement channel defined as $\E(\rho) = \sigma_0$ for all states $\rho$.
For simplicity, we restrict analysis to $\sigma$-fragments, where $\sigma$ is full-rank.

@@

It can further be seen that the maximum of $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment and directly related to the state sum-negativity $\sn{\rho}$ \nick{CITE}, defined as the sum of the negative components in $\W{\rho}$.
\begin{lemma}\label{lem:lcmax}
	Given a quantum state $\rho$, the maximum of its Lorenz curve $\lc{\rho}{\sigma}$ is independent of the $\sigma$--fragment in which it is defined and equal to $1+\sn{\rho}$.
\end{lemma}
\begin{proof}
	Borrowing the notation of~\cref{def:lc}, the derivative of the Lorenz curve $\lc{\rho}{\sigma}$ is
	\begin{equation}
		\frac{\rm{d}}{\rm{d}x} \lc{\rho}{\sigma}(x) = (\bmu^\downarrow)_i,\ x \in (x_{i-1}, x_i],
	\end{equation}
	for all $i=1,\dots,d^2$.

	Note that all components of $\W{\sigma}$ are positive, so $(\bmu^\downarrow)_i \geq 0$ if and only if $(\W{\rho})_i \geq 0$ for any $i=1,\dots,d^2$.

	Suppose all components of $\W{\rho}$ are non-negative.
	Then, $\sn{\rho}=0$ and the global maximum of the Lorenz curve is dictated by the normalisation of $\W{\rho}$ so we trivially have
	\begin{equation}
		\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 = 1 + \sn{\rho}.
	\end{equation}

	Suppose that $\W{\rho}$ has at least one negative component.
	Let $k$ be the index of the smallest non-negative component of $\bmu^\downarrow$.
	Then the maximum of the Lorenz curve $\lc{\rho}{\sigma}$ occurs at $x_k$, just before its slope becomes negative. 
	The $x$-coordinate $x_k$ is different for different $\sigma$--fragments but the value of the maximum is the same and is given by
	\begin{align}
		&\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}
		= \lc{\rho}{\sigma}(x_k)
		= \sum\limits_{i=1}^k (\W{\rho})_{\pi(i)} \\
		&= \sum\limits_{\bmx: \W[\bmx]{\rho} \geq 0} \W[\bmx]{\rho}
		= 1 + \sum\limits_{\bmx: \W[\bmx]{\rho} < 0} \abs{\W[\bmx]{\rho}} \\
		&= 1 + \sn{\rho}.
	\end{align}

We stress that $0 \leq \lc{\rho}{\sigma}(x) \leq 1$ for all $x \in [0,1]$ if and only if $\rho$ is a positive Wigner state.
The maximum of the Lorenz curve corresponds to the well established monotone of sum-negativity ($\rm{sn}$) further discussed in \nick{expand - move subsection on monotones (\cref{sec:mono}) in intro}.
Moreover, the area $\A_\sigma(\rho)$ of the function $L_{\rho|\sigma}$ above the line $y=1$ is also a resource monotone in the $\sigma$--fragment. 
This is clear because for any state conversion $\rho \longrightarrow \tau$ for some $\E \in \O_\sigma$, the Lorenz curve $L_{\tau|\sigma}$ is lower than $L_{\rho|\sigma}$, hence $\A_\sigma(\E(\rho)) \leq \A_\sigma(\rho)$.
The exact form of the monotone is given in~\cref{app:areamono}

@@

Any quantum circuit aiming at a given magic state conversion $\rho \longrightarrow \tau$ possesses certain symmetries according to~\cref{thm:frag} that allow us to study the conversion within only certain $\sigma$-fragments.
As a simple example, the dephasing channel
\begin{equation}\label{eq:dephase}
	\Delta(\rho) = \sum_{k \in \zd} \ketbra{k}{k}\rho\ketbra{k}{k}
\end{equation}
removes coherent phases in the computational basis and therefore leaves exactly all mixtures of computational basis states invariant.
A model circuit consisting only of such dephasing channels can be fully analysed in the $\sigma$--fragments for the pure computational basis states $\sigma$ \nick{as seen in a theorem in the appendix}.

@@

Consider a general magic state interconversion in $\O_\sigma$, $\rho \xrightarrow{\E \in \O_\sigma} \tau$.
It is shown in~\cref{app:major} that mana is an additive monotone in every $\sigma$--fragment under $d$--majorization, so it provides a necessary condition for the process to be possible,
\begin{equation}\label{eq:manabound}
    \mana{\rho} \geq \mana{\tau}. %{\rm{C}}_{\rm{mana}}(\rho, \tau, \sigma):\ 
\end{equation}
A new bound can be obtained in the $\sigma$--fragment by comparing the Lorenz curves of the initial and target states,
\begin{equation}\label{eq:majbound}
    \lc{\rho}{\sigma}(x) \geq \lc{\tau}{\sigma}(x),\ x\in [0,1].
\end{equation}
If condition ${\rm{C}}_{\rm{maj}}$ is not satisfied, then the Lorenz curve of initial state $\rho$ is below the curve of target $\tau$ at some point $x$ and the conversion is not possible.

In fact, our current setting makes it apparent that the mana condition is always weaker than the majorization condition for all magic state interconversions.
\begin{theorem}\label{thm:bounds}
    Given a magic state conversion $\rho \longrightarrow \tau$, the majorization condition is stronger than the mana condition in all $\sigma$--fragments.
\end{theorem}
\begin{proof}
    The maximum of the Lorenz curve of a state $\rho$ is independent of the $\sigma$--fragment due to~\cref{lem:lcmax}, and can be expressed as an increasing function of mana,
    \begin{equation}
        \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} = 1 + \sn{\rho} = \frac{1}{2} \left( 1 + e^\mana{\rho} \right).
    \end{equation}
    Therefore, the $\W{\sigma}$--majorization bound
    \begin{equation}
    	\lc{\rho}{\sigma}(x) \geq \lc{\rho}{\sigma}(x),\ x\in[0,1]
    \end{equation}
    implies the order $\max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)} \geq \max_{x\in[0,1]}{\lc{\rho}{\sigma}(x)}$ which is equivalent to the mana bound $\mana{\rho} \geq \mana{\tau}$.

@@

Of practical importance are magic state distillation (MSD) processes of the form
\begin{equation}\label{eq:distprocess}
    \rho^{\otimes k} \xrightarrow{\E \in \O_\sigma} \tau,
\end{equation}
where $k$ copies of a noisy magic state $\rho$ are converted into a target single-copy state $\tau$. \nick{expand?}

In general, the Wigner components of a $k$-copy state $\rho^{\otimes k}$ can be calculated, along with their multiplicities, from $W_\rho$ by expanding the terms in the multinomial expansion $\left( \sum_{\bm{z} \in \cal{P}_d} W_\rho(\bm{z}) \right)^n$.
This follows from the multiplicativity of the Wigner distribution.

As an example, consider a qutrit distillation process involving the Strange state $\ketbra{\rm{S}}$ depicted in~\cref{fig:strange}. 
It is the simplest non-trivial case to analyse, since the Strange state only has two distinct components $\left\{ -\frac{1}{3}, \frac{1}{6} \right\}$ with multiplicities $1$ and $8$ respectively.
Calculating the binomial expansion for the components of $\ket{S}\bra{S}^{\otimes k}$ gives $\{(-1)^j 2^{j-k} 3^{-k}\}_{0 \leq j \leq k}$ with multiplicity $8^{k-j} \binom{k}{j}$ for the $j$-th term.
This allows analytical calculation of all Lorenz curve points, hence the maximum of the $k$-copy state is
\begin{equation}\label{eq:Skmax}
    \max_{x\in [0,1]}{\lc{\ketbra{S}^{\otimes k}} {\sigma}}(x) = 1 + \left(\frac{4}{3}\right)^k \sum\limits_{j=0}^{\floor{\frac{k-1}{2}}} 4^{-(2j+1)} \binom{k}{2j+1}.
\end{equation}
\ddd{[We can probably put upper and lower bounds on this value fairly readily. E.g. using known sum rules.]}

Consider the noisy Strange state,
\begin{equation}
    \rho_{\rm{S}}(\epsilon) = (1 - \epsilon) \ket{\rm{S}}\bra{\rm{S}} + \epsilon \sigma,
\end{equation}
in $\O_\sigma$.
At noise levels $\epsilon \geq \frac{3}{4}$, the state is sufficiently noisy so as the Wigner distribution $\W{\rho_{\rm{S}}(\epsilon)}$ no longer contains negativities. 
At any $\epsilon \leq \frac{3}{4}$, we can investigate the distillation process resulting in a single-copy state with sufficiently low target $\epsilon_{\tau}$,
\begin{equation}\label{eq:sdist}
	\rho_{\rm{S}}(\epsilon)^{\otimes k} \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(\epsilon_{\tau})
\end{equation}

The more noisy the initial state is, the more copies needed to reach the target, therefore it makes sense to define a noise level threshold
\begin{equation}\label{eq:ethresh}
	\epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma) \coloneqq \sup{\{\epsilon:\ \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}},
\end{equation}
so that the MSD process~(\ref{eq:sdist}) is impossible for all $\epsilon > \epsilon_{\rm{th}}(k, \epsilon_\tau, \sigma)$

\nick{Condition in~\cref{eq:ethresh} is informally written. Can also define 
\begin{equation}\label{eq:ethresh}
	k_{\rm{th}}(\epsilon, \epsilon_\tau, \sigma) \coloneqq \min{\{k:\ k \in \mathbb{N}, \lc{\rho_{\rm{S}}(\epsilon)^{\otimes k}}{\sigma} \geq \lc{\rho_{\rm{S}}(\epsilon_{\tau})}{\sigma}\}}.
\end{equation}}
We now examine the MSD process~(\ref{eq:sdist}) in greater detail for some important $\sigma$--fragments.

\subsection{Magic in unital fragments}\label{sec:thermal}

Magic state distillation circuits in principle consist of bulk sequences of random Clifford unitaries ($\rcu$)\nick{CITE}, depicted in~\cref{fig:zoo}.
Operations in $\rcu$ can be expressed as
\begin{equation}
    \E(\rho) = \sum_i p_i U_i \rho U_i^\dagger,\ U_i \in \cd.
\end{equation}
Depending on the symmetries of such operations, a sequence of them may belong in various $\sigma$--fragments and the majorization condition~(\ref{eq:majbound}) needs to be checked in all these $\sigma$-fragments that reflect the symmetries of the operation sequence.
However, they always belong to the \emph{unital fragment} $\O_{\frac{1}{d}\id}$

If one incorporates noisy channels in the circuit, for example dephasing channels as in~\cref{eq:dephase} in various bases, symmetries are reduced.
Dephasing channels and general bit-flip error channels are examples of the many error-inducing channels that respect the unital symmetry. \nick{expand}

\nick{Replace the following with discussion of MSD process in the unital fragment for various numbers of copies $k$ vs mana}

In~\cref{fig:distill}, we examine the purifying process 
\begin{equation}\label{eq:purify}
    \rho_{\rm{S}}^{\otimes k}(\epsilon_{\rm{th}}) \xrightarrow{\E \in \O_\sigma} \rho_{\rm{S}}(0.05),\ \sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id
\end{equation}
with $\epsilon_{\rm{th}}$ being the noise level threshold that does not prohibit the process for given number of copies $k$ and $\sigma$--fragment, parametrised by $p$ as a mixture of the zero and the maximally mixed states.
Thresholds provided by Lorenz curve comparison are always much stricter than mana thresholds.
\begin{figure}
    \centering
    \includegraphics[scale=0.5]{figs/ratios.pdf}
    \caption{\textbf{Noise threshold ratios.} Mana and Lorenz curve ratios for the Strange state purifying process in~\cref{eq:purify}.
    The ratios are calculated for different numbers of initial state copies and different $\sigma$--fragments parametrised by $p$ such that $\sigma = (1-p)\ketbra{0} + p \frac{1}{3}\id$.
    Lorenz curve comparison consistently gives stricter bounds as proven in~\cref{thm:bounds}.
    \nick{Consider set of pure stabilizer states instead of $(1-p)\ketbra{0} + p \frac{1}{3}\id$ perhaps}
    }
    \label{fig:distill}
\end{figure}

\subsection{Magic in thermal fragments}\label{sec:thermal}

Consider a system driven by Hamiltonian $H$ and a circuit consisting of thermal operations.
The computational basis now coincides with the energy eigenbasis of Hamiltonian $H$.
We denote the thermal state $\gamma_\beta = \frac{e^{-\beta H}}{\Z_\beta}$, where $\Z_\beta = \tr[e^{-\beta H}]$.\nick{expand}

Thermal operations coincide with fragment $\O_{\gamma_\beta}$ \nick{expand}
The Wigner distribution of thermal state $\gamma_\beta$ always consists of strictly positive components,
\begin{equation}
	\W[\bmx]{\gamma_\beta} = \frac{e^{-\beta \epsilon_{x_0}}}{d\Z_\beta}\ \text{for all}\ \bmx \in \pd,
\end{equation}
so pre-order $\prec_{\gamma_\beta}$ is well defined.

We generalise the analysis of~\cref{sec:unital} \nick{expand}.
\nick{Include figure with noise threshold level $\epsilon_{\rm{th}}$ in $y$-axis and temperature $\beta$ in $x$-axis. for various numbers of copies $k$.}
